Comparing Parallel Sorting Algorithms on a High Performance Computing Cluster Using OpenMP

### 2020-11-16 paper/Paper.tex
Added appendix content

    This suggests that there is significant overhead with smaller array sizes, but this is overcome by efficeicny gains on larger array sizes. 
    \section{Conclusion}
    % TODO these are what we expect to see...
    As expected, the three $O(n log(n))$ algorithms perform better then Insertion sort. 
    Due to the more parallel nature of Quicksort and Mergesort, these algorithms benefit more from parallization then the more sequential Heapsort. 
    This is because the divide and conquer strategy is inherently more parallel, which should be taken into account when developing new algorithms to be run on parallel and distributed computing platforms. 
    % TODO further findings from implementation
    \bibliography{ref.bib}
    \bibliographystyle{ieeetran}
    \appendix
    % TODO slap the code in here
\end{document}

>>>>

    This suggests that there is significant overhead with smaller array sizes, but this is overcome by efficeicny gains on larger array sizes. 
    \section{Conclusion}
    % TODO these are what we expect to see...
    As expected, the three $O(n log(n))$ algorithms perform better then Insertion sort. 
    Due to the more parallel nature of Quicksort and Mergesort, these algorithms benefit more from parallization then the more sequential Heapsort. 
    This is because the divide and conquer strategy is inherently more parallel, which should be taken into account when developing new algorithms to be run on parallel and distributed computing platforms. 
    % TODO further findings from implementation
    \bibliography{ref.bib}
    \bibliographystyle{ieeetran}
    \appendix
	All of our code and data can be found in our GitHub repo \href{https://github.com/causeyc/csds438_sorting}{here}. Our implementation of parallel Mergesort is located in mergesort/merge$\_$sort$\_$OpenMP.c. The parallel Quicksort implementation is in quicksort/quicksortOMP.c. Our serial Heapsort implementation is located in heapsort/heapsort.c. In order to run the experiment, clone the repo into a location on Case Western's HPC Markov cluster. From there, run the SLURM batch scripts. The first is \textbf{sorting.slurm} and is located in mergesort/. This script runs parallel Mergesort on a compute node on all combinations of array sizes and CPU core numbers (as explained in the main part of the paper). Once finished, an output SLURM file will be produced that contains the execution times of sorts. \textit{Mutatis mutandis} for Quicksort (the batch script is called \textbf{qs-job.slurm} and is located in quicksort/).
    % TODO slap the code in here
\end{document}
